PANCHANGE_analysis

### 2020-08-24 PANCHANGE_analysis.Rmd
gad change stratification

@@

For each item 
present percentages of how say that this is due to the pandemic 
```{r}
pcl.retro.items <- c(
  "pcl.stressful_experience_upset_reminded_retro_numeric",
  "pcl.stressful_experience_repeated_images_retro_numeric",
  "pcl.stressful_situation_avoiding_activities_retro_numeric",
  "pcl.cut_people_feeling_distant_retro_numeric",
  "pcl.difficulty_concentrating_retro_numeric",
  "pcl.feeling_irritable_or_having_angry_outbursts_retro_numeric"
)

>>>>

### Split sample in improvement and worsening
```{r gad improvment worsening stratification}
dat <- dat %>%
  mutate(gad.change_binary_numeric =
           case_when(
             gad.pandemic_felt_feelings_numeric == 1 ~ 1,
             gad.pandemic_felt_feelings_numeric == 2 ~ 1,
             gad.pandemic_felt_feelings_numeric == 3 ~ 0,
             gad.pandemic_felt_feelings_numeric == 4 ~ 2,
             gad.pandemic_felt_feelings_numeric == 5 ~ 2
           )
         )

dat <- dat %>%
  mutate(gad.change_binary =
           recode_factor(
             gad.change_binary_numeric,
             `1` = "Worsening",
             `2` = "No change",
             `3` = "Improvement"
           )
         )

dat %>%
  freq(gad.change_binary)
```

```{r}
dat %>%
  freq(gad.pandemic_felt_feelings_numeric)
```

@@

For each item 
present percentages of how say that this is due to the pandemic 
```{r pcl percentages due to pandemic}
pcl.retro.items <- c(
  "pcl.stressful_experience_upset_reminded_retro_numeric",
  "pcl.stressful_experience_repeated_images_retro_numeric",
  "pcl.stressful_situation_avoiding_activities_retro_numeric",
  "pcl.cut_people_feeling_distant_retro_numeric",
  "pcl.difficulty_concentrating_retro_numeric",
  "pcl.feeling_irritable_or_having_angry_outbursts_retro_numeric"
)
